MsCcHSFeed Outline

### 2022-02-25 MsCcHSFeedOutlineDec15.Rmd
Made table 1 and deleted extraneous stuff

```{r}
library(ggplot2)
library(tidyverse)
library(Rmisc)
library(lubridate)
library(lmerTest)
```

@@

```{r}
waspplot <- ggplot(data = datawasp, aes(x = food, y = percent)) +
  theme_bw() + 
  geom_boxplot() + 
  geom_jitter(aes(color = treatment), width = 0.1, height = 0) + 
  labs(x = "Hostplant", y = "Percent survival from emergence to eclosion", color = "Treatment")

waspplot

ggsave("~/Desktop/GitHub/MsCcHSFeed/Figs/waspplot.png", plot = waspplot, width = 8, height = 5)

@@

```{r}
waspbinom2 <- glm(percent ~ food, family = "binomial", weights = num.w.tot, 
                  data = datawasp[datawasp$treatment == "P NHS", ])

summary(waspbinom2)

anova(waspbinom2, test = "Chisq")

@@

>>>>

```{r}
library(ggplot2)
library(tidyverse)
#library(Rmisc)
library(lubridate)
library(lmerTest)
```

@@

@@

@@

# Table 1: Mean percent eclosion success

```{r}
eclosmeans <- datawasp %>%
  group_by(food, treatment) %>%
    summarise(mean = mean(percent))

eclosmeans
```
